|

### 2022-06-16 appendix/appendix-short.Rmd
add pdfs
Signed-off-by: Danilo Freire <danilofreire@gmail.com>

---
title: |
       | Supplementary Material for "Vigilantism and Institutions: Understanding Attitudes toward Lynching in Brazil"
author:
- "Danilo Freire[^freire]"
- "David Skarbek[^skarbek]"
date: 14 June 2022
fontfamily: libertine
fontawesome: yes
fontsize: 12pt
monospace-url: yes
spacing: double
papersize: a4paper
bibliography: ../article/references.bib
biblio-style: ../article/chicago-ff.bst
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    highlight: haddock
    toc: true
    toc_depth: 3
    keep_tex: no
    template: template.latex
---

@@

We ran our survey experiments from October 30 to December 14 via Qualtrics. Our
sample includes `r nrow(df1)` Brazilians older than 18 years of age from the
five regions of the country (Center-West, North, Northeast, South, and
Southeast).

>>>>

---
title: |
       | Supplementary Material for "Vigilantism and Institutions: Understanding Attitudes toward Lynching in Brazil"
author:
- "Danilo Freire[^freire]"
- "David Skarbek[^skarbek]"
date: \today
fontfamily: libertine
fontawesome: yes
fontsize: 12pt
monospace-url: yes
spacing: double
papersize: a4paper
bibliography: ../article/references.bib
biblio-style: ../article/chicago-ff.bst
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    highlight: haddock
    toc: true
    toc_depth: 3
    keep_tex: no
    template: template.latex
---

@@

We ran our survey experiments from October 30 to December 14, 2020 via
Qualtrics. Our sample includes `r nrow(df1)` Brazilians older than 18 years of
age from the five regions of the country (Center-West, North, Northeast, South,
and Southeast).
